\documentclass[12pt]{article}
% General packages
\usepackage{amsmath, graphicx, float, tabularx, booktabs, color}
% For adjusting margin size
\usepackage[margin=1in]{geometry}
% For setting bookmarks on pdf export
\usepackage[bookmarks,bookmarksopen,bookmarksdepth=2]{hyperref}
% For codeblocks
\usepackage{listings}
\usepackage{cite}

%Define Colors
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

% Difine diff language
\lstdefinelanguage{diff}{
  morecomment=[f][\color{blue}]{@@},     % group identifier
  morecomment=[f][\color{red}]-,         % deleted lines 
  morecomment=[f][\color{green}]+,       % added lines
  morecomment=[f][\color{magenta}]{---}, % Diff header lines (must appear after +,-)
  morecomment=[f][\color{magenta}]{+++},
}


% Color Code
\lstset{frame=tb,
  language=ruby,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=4
}

% Image path location
\graphicspath{ {images/} }

\begin{document}

% Title information
\title{Buffer Overflow SLMail5.5.0 Service and Gain Root Shell}
\author{Devin Trejo \tabularnewline devin.trejo@temple.edu }
\date{\today}
\maketitle

\section{Summary}
\label{sect:summary}


\section{Introduction}
\label{sect:intro}
\subsection{Background SLMail5.5.0}
\label{sec:background}

\subsection{Attack Approach}
\label{sec:approach}
\subsection{Finding Size of Password Buffer}
\label{sec:approachpassbuff}
The first step for this attack is to find the size of the SLMail 5.5.0
password buffer.

Modify your script to send a username and a password to the POP3 port.  
Be sure to receive the reply and print it after the username and password 
are sent.

Now modify the script again.  Create an array of buffers, each longer than 
the previous.  You can fill them with the letter "A" like I did in class 
when I demonstrated the buffer overflow.  The idea is to fuzz the password 
field during the login process.  For each string in the buffer, send the 
PASS command along with the buffer.  Attach your script a debugger when 
doing this.  You are looking to overwrite the EIP register (by overflowing 
the buffer).  How long does the buffer in your array need to be to
overwrite EIP?


\section{Discussion}
\label{sect:discussion}


\section{Conclusion}
\label{sect:conclusion}


\nocite{*}
\bibliographystyle{IEEEtran}
\bibliography{20160404_biblo.bib}

\section*{Appendix}
\label{sect:appendix}

\end{document}